### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

\revise{
By Theorem~\ref{thm-tsim-radius}, we know that $P$ matches a ball $\ball{[v, t]}$ ($t \in [1,r-1]$), only when $P$ matches ball $\ball{[v, r]}$ via graph simulation,
and the match results for $\ball{[v, t]}$ can be derived from the matches for $\ball{[v, r]}$.
Therefore, we only concern about balls $\ball{[v, r]}$ in the incremental process, and finally compute the matches for balls $\ball{[v, t]}$ after we get the matches for ball $\ball{[v, r]}$.
Note that in the following when we refer to a ball, we indicate the ball with radius $r$ by default.}

@@

\stitle{Incremental complexity analysis}. As observed in~\cite{Reps96}, the complexity of an incremental algorithm should be measured by the size $|\aff|$ of {\em the changes} in the input and output, rather than the entire input, to measure the amount of work absolutely necessary to be performed for the problem.

An incremental problem is said to be {\em bounded} if it can be solved by an algorithm whose complexity is a function of $|\aff|$ alone, and {\em unbounded}, otherwise.
Unfortunately, \dynteamF\, is unbounded, similar to the observations in \cite{FanLMTWW10,FanWW13-tods}.

\begin{prop}
\label{thm-inc-grouprec-pat}
The \dynteamF\, problem is unbounded, even for $k$ = 1 and unit pattern or data updates.
\end{prop}

\begin{example}
\label{exm-pattern-challenge}
Continue Example~\ref{exm-motivation-inc}, and consider updates $\Delta P_1$ or $\Delta G_1$ that obviously may introduce new matches.
%For convenience of presentation, we treat $\Delta P_1$ and $\Delta G_1$ separately.

\sstab
(1) For $\Delta P_1$, $\ball{[\kw{PM_1}, 2]}$ already matches $P$, and may produce more matched nodes for $P_1\oplus \Delta P_1$,
thus a re-computation for perfect subgraphs in the ball is needed.
For all other balls, $\Delta P_1$ may turn unmatched nodes to matched and may produce perfect subgraphs,
thus re-computation is also needed.
\looseness=-1

\sstab
(2) For $\Delta G_1$, it produces a new perfect subgraph for $P$ in $G_1\oplus\Delta G_1$,
\ie the connected component containing \kw{PM_2}.
The question is how to directly find new and maintain previous answers without redundant computation.
\looseness=-1
\end{example}

@@

\subsection{A Unified Incremental Approach}
%\label{subsec-framework}

>>>>

By Theorem~\ref{thm-tsim-radius}, pattern $P$ matches a ball $\ball{[v, t]}$ ($t \in [1,r-1]$), only if $P$ matches ball $\ball{[v, r]}$ via graph simulation,
and the match results for $\ball{[v, t]}$ can be derived from the matches for $\ball{[v, r]}$.
Therefore, the key of the incremental computation is to deal with the balls $\ball{[v, r]}$ with radius $r$.
In the sequel, a ball has a radius $r$ by default.

@@

We first analyze the inherent computational complexity of the dynamic top-$k$ team formation.

\stitle{Incremental complexity analysis}. As observed in~\cite{Reps96,inc-survey}, the complexity of incremental algorithms should be measured by the size $|\aff|$ of {\em the changes} in the input and output, rather than the entire input, to measure the amount of work essentially to be performed for the problem.

An incremental problem is said to be {\em bounded} if it can be solved by an algorithm whose complexity is a function of $|\aff|$ alone, and is {\em unbounded}, otherwise. Unsurprisingly, the dynamic top-$k$ team formation problem is unbounded, similar to the other extensions of graph simulation \cite{FanLMTWW10,FanWW13-tods}.

\begin{prop}
\label{thm-inc-grouprec-pat}
The \dynteamF{} problem is unbounded, even for $k$ = 1 and unit pattern or data updates.
\end{prop}

We then illustrate the impact of pattern and data updates on the matching results.

\begin{example}
\label{exm-pattern-challenge}
Continue Example~\ref{exm-motivation-inc} with $\Delta P_1$ and $\Delta G_1$.

% that obviously may introduce new matches.
%For convenience of presentation, we treat $\Delta P_1$ and $\Delta G_1$ separately.

\sstab
(1) For $\Delta P_1$, $\ball{[\kw{PM_1}, 2]}$ already matches $P$, and may produce more matched nodes for $P_1\oplus \Delta P_1$,
thus a re-computation for perfect subgraphs is needed.
For all other balls, $\Delta P_1$ may turn unmatched nodes to matched and may produce perfect subgraphs,
thus re-computation is also needed.

\sstab
(2) For $\Delta G_1$, it produces a new perfect subgraph for $P$ in $G_1\oplus\Delta G_1$,
\ie the connected component having \kw{PM_2}.
%The question is how to directly find new and maintain previous answers without redundant computation.
\end{example}

@@

\subsection{Unified Incremental Framework}
%\label{subsec-framework}
